TrueSkill Through Time: the \proglang{Python} Package

### 2020-07-20 article.tex
Biblio mati
TTT: agrego formato algoritmos

@@

>>>>

\usepackage{listings}
\lstset{
  language=Python,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=true,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=4
}

@@

\begin{algorithm}[H]
  \caption{Posterior for Linear Regression Model}
  \label{alg:posterior_for_linear_regression_model}
  \lstinputlisting{code/ejemplo.py}
\end{algorithm}
